---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# groupByCols

<!-- badges: start -->
<!-- badges: end -->

The goal of groupByCols is to summarize the percentage of rows that satisfies given condition(s) by group

## Installation

You can install the development version of groupByCols like so:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-czz1997", ref = "0.1.1")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## load the function
library(groupByCols)
## load other packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(datateachr))
```

Calculate the percentage of buildings that has a sprinkler system by year:
```{r}
apt_buildings %>%
    filter(year_built >= 1950) %>%
    percentage_by_group('year_built', sprinkler_system == "YES")
```

Calculate the percentage of buildings that has at least 5 floors by year and property type:
```{r}
apt_buildings %>%
    filter(year_built >= 1950) %>%
    percentage_by_group(c('year_built', 'property_type'), no_of_storeys >= 5)
```
